---
title: "hw01_gapminder"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Requirement of the Assignment

Make an R Markdown document that explores a dataset, such as gapminder seen in class. You don't need an extensive exploration in order to get a good grade here; a basic one will do, not unlike the one done in class, which would be considered sufficient (but less so the more verbatim your submission is). Render your R Markdown to the github_document output format. Commit both the .Rmd and .md files and push them to GitHub.

#load the Gapminder database 

```{r}
library(gapminder)
```


#structure of the object
```{r}
str(gapminder)
```

#explore the database with different functions
```{r}
class(gapminder)
head(gapminder) ## return the first part of the database
tail(gapminder) ## return the lsat part of the database
names(gapminder)  ## get the name of the object
length(gapminder) ## get the length of the factor
nrow(gapminder) ## number of rows in the database
summary(gapminder) ## statistical overview
```

#Extract data  from the database for analysis
```{r}
mean(gapminder$lifeExp) ## mean of the lifeExp
median(gapminder$year) ## median of the year
var(gapminder$pop) ## variance of population
```


#visualising the data
```{r}
plot(lifeExp ~ year, gapminder)  ## plot the graph of lifeExp against the year
```{r}